---
title: "CV Highlights"
execute: {echo: false, warning: false, message: false}
engine: knitr
---


## Education
- PhD in Molecular and Cellular Biology — focus on genetics, genomics, and computational biology.
- Continued education in bioinformatics, statistics, and advanced molecular methods.


## Distinctions & Memberships
- Research funding contributions > **€36 M** (PI/Co-I/Researcher).  
- Collaborations with EMBRAPA (Brazil), Cardiff University (UK), and University of Coimbra (PT).

## Career (Professional Experience)
```{r}
library(readxl); library(dplyr); library(knitr)
path <- "data/cv.xlsx"
read_excel(path, sheet = "Professional_Experience") %>% knitr::kable()
```

## Education
```{r}
read_excel("data/cv.xlsx", sheet = "Education") %>% knitr::kable()
```

## Additional Education & Courses
```{r}
read_excel("data/cv.xlsx", sheet = "Additional_Education") %>% knitr::kable()
```

## Memberships
```{r}
read_excel("data/cv.xlsx", sheet = "Memberships") %>% knitr::kable()
```

## Distinctions (Awards)
```{r}
read_excel("data/cv.xlsx", sheet = "Distinctions") %>% knitr::kable()
```

## Other Skills
```{r}
read_excel("data/cv.xlsx", sheet = "Other_Skills") %>% knitr::kable()
```
