---
title: "Scientific Performance"
execute: {echo: false, warning: false, message: false}
---

## Scientific Output - Eval. Criterion 5.1.1 of the Call

### Publications (n=41)
```{r}
library(readxl); library(knitr); library(dplyr)
path <- "data/cv.xlsx"
df <- read_excel(path, sheet = "Publications")
if ("URL" %in% names(df)) {
	df$URL <- ifelse(!is.na(df$URL) & nzchar(df$URL), paste0("[link](", df$URL, ")"), "")
}
knitr::kable(df, escape = FALSE, longtable = TRUE)
```

### Chapters (n=2)
```{r}
df <- read_excel("data/cv.xlsx", sheet = "Chapters")
if ("URL" %in% names(df)) {
	df$URL <- ifelse(!is.na(df$URL) & nzchar(df$URL), paste0("[link](", df$URL, ")"), "")
}
knitr::kable(df, escape = FALSE, longtable = TRUE)
```

### Technical Publications (n=4)
```{r}
df <- read_excel("data/cv.xlsx", sheet = "Technical_Publications")
if ("URL" %in% names(df)) {
	df$URL <- ifelse(!is.na(df$URL) & nzchar(df$URL), paste0("[link](", df$URL, ")"), "")
}
knitr::kable(df, escape = FALSE, longtable = TRUE)
```

### Preprints (n=6)
```{r}
df <- read_excel("data/cv.xlsx", sheet = "Preprints")
if ("URL" %in% names(df)) {
	df$URL <- ifelse(!is.na(df$URL) & nzchar(df$URL), paste0("[link](", df$URL, ")"), "")
}
knitr::kable(df, escape = FALSE, longtable = TRUE)
```

### Other Publications
```{r}
df <- read_excel("data/cv.xlsx", sheet = "Other_Publications")
if ("URL" %in% names(df)) {
	df$URL <- ifelse(!is.na(df$URL) & nzchar(df$URL), paste0("[link](", df$URL, ")"), "")
} 
knitr::kable(df, escape = FALSE, longtable = TRUE)
```

### Conference Proceedings (n=17)
```{r}
df <- read_excel("data/cv.xlsx", sheet = "Conference_Proceedings")
if ("URL" %in% names(df)) {
	df$URL <- ifelse(!is.na(df$URL) & nzchar(df$URL), paste0("[link](", df$URL, ")"), "")
}
knitr::kable(df, escape = FALSE, longtable = TRUE)
```

### Oral Presentations (n=27)
```{r}
df <- read_excel("data/cv.xlsx", sheet = "Oral_Presentations")
if ("URL" %in% names(df)) {
	df$URL <- ifelse(!is.na(df$URL) & nzchar(df$URL), paste0("[link](", df$URL, ")"), "")
}
knitr::kable(df, escape = FALSE, longtable = TRUE)
```

### Posters (n=35)
```{r}
df <- read_excel("data/cv.xlsx", sheet = "Posters")
if ("URL" %in% names(df)) {
	df$URL <- ifelse(!is.na(df$URL) & nzchar(df$URL), paste0("[link](", df$URL, ")"), "")
}
knitr::kable(df, escape = FALSE, longtable = TRUE)
```


## Participation in Research Projects - Eval. Criterion 5.1.2 of the Call

### Approved Projects (n=32)
```{r}
df <- read_excel("data/cv.xlsx", sheet = "Projects")
if ("URL" %in% names(df)) {
	df$URL <- ifelse(!is.na(df$URL) & nzchar(df$URL), paste0("[link](", df$URL, ")"), "")
}
knitr::kable(df, escape = FALSE, longtable = TRUE)
```

### Non‑approved Projects (n=23)
```{r}
df <- read_excel("data/cv.xlsx", sheet = "Non_Approved_Projects")
if ("URL" %in% names(df)) {
	df$URL <- ifelse(!is.na(df$URL) & nzchar(df$URL), paste0("[link](", df$URL, ")"), "")
}
knitr::kable(df, escape = FALSE, longtable = TRUE)
```

## Service to the Scientific Community - Eval. Criterion 5.1.3 of the Call

### Event Organisation (n=14)
```{r}
df <- read_excel("data/cv.xlsx", sheet = "Event_Organisation")
if ("URL" %in% names(df)) {
	df$URL <- ifelse(!is.na(df$URL) & nzchar(df$URL), paste0("[link](", df$URL, ")"), "")
}
knitr::kable(df, escape = FALSE, longtable = TRUE)
```

### Peer Review (n=13 diff Journals)
```{r}
df <- read_excel("data/cv.xlsx", sheet = "Peer_Review")
if ("URL" %in% names(df)) {
	df$URL <- ifelse(!is.na(df$URL) & nzchar(df$URL), paste0("[link](", df$URL, ")"), "")
}
knitr::kable(df, escape = FALSE, longtable = TRUE)
```

### Project Evaluation Panels (n=4)
```{r}
df <- read_excel("data/cv.xlsx", sheet = "Project_Evaluation_Panels")
if ("URL" %in% names(df)) {
	df$URL <- ifelse(!is.na(df$URL) & nzchar(df$URL), paste0("[link](", df$URL, ")"), "")
}
knitr::kable(df, escape = FALSE, longtable = TRUE)
```

### Research Expeditions (n=8)
```{r}
df <- read_excel("data/cv.xlsx", sheet = "Research_Expeditions")
if ("URL" %in% names(df)) {
	df$URL <- ifelse(!is.na(df$URL) & nzchar(df$URL), paste0("[link](", df$URL, ")"), "")
}
knitr::kable(df, escape = FALSE, longtable = TRUE)
```

### Invited Oral Presentations (n=16)
```{r}
df <- read_excel("data/cv.xlsx", sheet = "Invited_Oral_Presentations")
if ("URL" %in% names(df)) {
	df$URL <- ifelse(!is.na(df$URL) & nzchar(df$URL), paste0("[link](", df$URL, ")"), "")
}
knitr::kable(df, escape = FALSE, longtable = TRUE)
```

### Jury (Academic Degree) (n=16)
```{r}
df <- read_excel("data/cv.xlsx", sheet = "Jury_Academic_Degree")
if ("URL" %in% names(df)) {
	df$URL <- ifelse(!is.na(df$URL) & nzchar(df$URL), paste0("[link](", df$URL, ")"), "")
}
knitr::kable(df, escape = FALSE, longtable = TRUE)
```

### Scientific Meetings (n=8)
```{r}
df <- read_excel("data/cv.xlsx", sheet = "Scientific_Meetings")
if ("URL" %in% names(df)) {
	df$URL <- ifelse(!is.na(df$URL) & nzchar(df$URL), paste0("[link](", df$URL, ")"), "")
}
knitr::kable(df, escape = FALSE, longtable = TRUE)
```

### External Services (n=4)
```{r}
df <- read_excel("data/cv.xlsx", sheet = "External_Services")
if ("URL" %in% names(df)) {
	df$URL <- ifelse(!is.na(df$URL) & nzchar(df$URL), paste0("[link](", df$URL, ")"), "")
}
knitr::kable(df, escape = FALSE, longtable = TRUE)
```

## Distinctions (Awards)
```{r}
read_excel("data/cv.xlsx", sheet = "Distinctions") %>% knitr::kable()
```

## Research Teams & Supervision - Eval. Criterion 5.1.4 of the Call
### PhD, Postdoc Supervisions and Technical Staff (n=9)
```{r}
df <- read_excel("data/cv.xlsx", sheet = "PhD&Postdoc&Tech_Supervisions")
if ("URL" %in% names(df)) {
	df$URL <- ifelse(!is.na(df$URL) & nzchar(df$URL), paste0("[link](", df$URL, ")"), "")
}
knitr::kable(df, escape = FALSE, longtable = TRUE)
```
## Other Relevant Activities

### Management & Coordination Roles (n=)
```{r}
df <- read_excel("data/cv.xlsx", sheet = "Management&Coordination_Roles")
if ("URL" %in% names(df)) {
	df$URL <- ifelse(!is.na(df$URL) & nzchar(df$URL), paste0("[link](", df$URL, ")"), "")
}
knitr::kable(df, escape = FALSE, longtable = TRUE)
```

### Outreach Activities
```{r}
df <- read_excel("data/cv.xlsx", sheet = "Outreach_Activities")
if ("URL" %in% names(df)) {
	df$URL <- ifelse(!is.na(df$URL) & nzchar(df$URL), paste0("[link](", df$URL, ")"), "")
}
knitr::kable(df, escape = FALSE, longtable = TRUE)
```
